Resource Buying Games

### 2017-03-31 paper.tex
added alg

\todo[done]{working iteratively towards a basis by prim's algorithm as example
to introduce cuts and contractions and deletions}
Consider the algorithm of Prim which computes spanning trees by iteratively

@@

in $\mathcal{S}$ and opens a dimensionality by connecting one of the graph
nodes. When an edge is added the result of the algorithm can only compute

@@

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game builds upon a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing. The algorithm
we present in the following chooses a basis for every player by iteratively
adding one element from a cut and contracting the matroid to the added element
while deleting all other elements from the cut. Since cuts are inclusion-wise
minimal deleting all but one element from one cut leaves at least one possible
basis for the player available. For every player we maintain the elements which
are chosen for her up to the current state (\emph{working basis}) and which
elements are still available to build her basis (\emph{ground-set}) and which
bases she can still use. Initially the working basis is empty and the
ground-set and available bases are taken from the matroid of the player. For
every resource we maintain the cost the next added load causes and how much
load already is placed upon the resource(\emph{current load}). Initially for
every resource $e$ the current load is zero and the next load causes $c_{e}(1)$
cost.

>>>>

\todo[done]{working iteratively towards a basis by kruskal's algorithm as
example to introduce cuts and contractions and deletions}
Consider the algorithm of Kruskal which computes spanning trees by iteratively

@@

in $\mathcal{S}$ and opens a dimensionality by connecting already computed
components.  When an edge is added the result of the algorithm can only compute

@@

\section{Unweighted Matroid Games with marginally non-increasing cost
functions}
We present an algorithm which computes pure Nash equilibria in unweighted
matroid games with marginally non-increasing cost functions. Firstly, an
unweighted matroid game builds upon a congestion model of the form
$\tupel{N, E, \mathcal{B} = \times_{i\in N}\mathcal{B}_{i},
(d_{i})_{i\in N}, (c_{e})_{e\in E}}$ where for all $i\in N$ holds $d_{i} = 1$
(unweighted) and every $\mathcal{B}_{i}$ is the set of bases for some matroid
$\mathcal{M}_{i} = \tupel{E_{i}, \mathcal{B}_{i}}$. The set of resources is
given by the matroids of the players $E = \bigcup_{i\in N}E_{i}$ and all cost
functions $c_{e}$ are marginally non-increasing.

The algorithm we present in the following chooses a basis for every player by
iteratively adding one element from a cut and contracting the matroid to the
added element while deleting all other elements from the cut. Since cuts are
inclusion-wise minimal deleting all but one element from one cut leaves at
least one possible basis for the player available. For every player we maintain
the elements which are chosen for her up to the current state
(\emph{working basis}) and which elements are still available to build her
basis (\emph{ground-set}) and which bases she can still use. Initially the
working basis is empty and the ground-set and available bases are taken from
the matroid of the player. For every resource we maintain the cost the next
added load causes and how much load already is placed upon the
resource(\emph{current load}). Initially for every resource $e$ the current
load is zero and the next load causes $c_{e}(1)$ cost. We can devide the
algorithm into four steps as presented in Figure \ref{alg:main}.
\begin{figure}
  \begin{tabular}{|lll|}
    \hline
    (i) & Init: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item \parbox{0.7\textwidth}{every player: empty working basis,
            complete ground-set, complete set of valid result bases}
          \item every resource: cost for next load, current load
        \end{itemize}
      }\\\hline
    (ii) & Find: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item inclusion-min (necessary cost)-max cut $C$
          \item minimal cost resource $e$ in $C$
          \item owner $i$ of $C$
        \end{itemize}
      }\\\hline
    (iii) & Pick: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item $i$: add $e$ to working basis, contract matroid to $e$
          \item $e$: update marginal cost and increase load
          \item all player: delete elements $C\setminus\set{e}$ from matroid
        \end{itemize}
      }\\\hline
    (iv) & Break: &\hspace{-0.6cm}\parbox{0.8\textwidth}{
        \begin{itemize}
          \item exists player with incomplete basis: goto (ii)
          \item otherwise: return chosen bases and payments
        \end{itemize}
      }\\\hline
  \end{tabular}
  \caption{Algorithm to compute a PNE for unweighted matroid games with
    marginally non-increasing cost functions. Note that in step (ii) only
    inclusion-wise minimal cuts are considered (specifically the one for which
    minimal cost of all elements in the cut is maximal over all considered cuts
    is chosen). Restricting the selection to inclusion-wise minimal cuts
    ensures that removing all other elements preserves possible bases for
    \emph{all} players}
  \label{alg:main}
\end{figure}
By induction on the iterations one can prove that the cost of the chosen
element in step (ii) always decreases. This is a key lemma to prove the
correctness of the algorithm. Because, if we assume to have a beneficial
alternative to the computed basis for one player there is an element with
less cost. This alternative element is not part of the selected cut since
it would be removed for all players and thus keep its marginal cost although
only elements with higher costs are removed (by choice of the element in the
cut). Furthermore, the alternative element cannot be available to the player
for which the cut is selected since both elements open the
\enquote{same dimensionality} in contradiction to choosing a cut. Thus, the
alternative element has been removed before which implies less cost in a
previous step to the iteration where the original element was chosen. This
contradicts the monotonicity of costs of considered elements through the
iterations. Thus
\begin{theo}
  The presented algorithm computes a PNE.
\end{theo}

\section{Weighted Matroid Games}
